---
title: "Week 10 Problem Set"
author: "Shyun Moon"
format: html
execute:
  echo: true
  warning: true
  message: true
---
#### Q1: Load and Inspect Data ------------------------------------

```{r}
## Load the saved dataset
experiment_data <- readRDS("../data/raw/experiment_data.rds")

## Take a quick look at the first few rows
head(experiment_data)

## Check the structure of the dataset
str(experiment_data)
```
#### Q2: Functions ------------------------------------------------
```{r}
## Generate one or more random numbers between min and max (defaults: one number between 1–10)

getRandomNumber <- function(min = 1, max = 10, number = 1) {
  sample(min:max, number)
}
```


```{r}
## Classify reaction times into "Fast", "Slow", or "Unknown" (default threshold = 500ms)

classify_rt <- function(rt, threshold = 500) {
  if(!is.numeric(rt)) {
    stop("Error: 'rt' must be numeric.")
  }
  if(!is.numeric(threshold) || length(threshold) != 1) {
    stop("Error: 'threshold' must be a single numeric value.")
  }
category <- ifelse(is.na(rt), "Unknown",
                     ifelse(rt < threshold, "Fast", "Slow"))
return(category)
}


```

#### Q3: Loops vs. Vectorization ------------------------------------------------
```{r}
## Q3.1 New Columns-----------------

experiment_data$age <- NA

## Q3.2 Loop Version ------------
## New column called "age" with random ages
for (i in 1:nrow(experiment_data)) {
  if(is.na(experiment_data[i, "age"])) {
    experiment_data[i, "age"] <- getRandomNumber(18, 65)
  }
}

head(experiment_data)

## Q3.3 Vectorized Version ---------
## Vectorized version of the command above

experiment_data$age <- sample(18:65, nrow(experiment_data), replace = TRUE)

head(experiment_data)

```
#### Q4: Control Structures on Data Frames ---------------------------
```{r}
## Q4.1 Loop ---------
## new column -> fill with Unknown if NA, otherwise, run classify_rt on rt and fill the new column accordingly

experiment_data$rt_category_loop <- NA

for (i in 1:nrow(experiment_data)) {
  if (is.na(experiment_data[i, "rt"])) {
    experiment_data[i, "rt_category_loop"] <- "Unknown"
  } else {
    experiment_data[i, "rt_category_loop"] <- classify_rt(experiment_data$rt[i])
  }
}


## Q4.2 Vectorized Version ---------

experiment_data$rt_category_vec <- NA

experiment_data$rt_category_vec <- ifelse(
  is.na(experiment_data$rt), "Unknown",
  classify_rt(experiment_data$rt)
)

## Q4.3 Compare the Two ---------
table(loop = experiment_data$rt_category_loop,
      vec  = experiment_data$rt_category_vec,
      useNA = "ifany")


```
#### Q5: Debugging Functions -----------------------------
```{r}
## Q5.1 Create Buggy Function -------
## function was reliant on global var

threshold <- 500

flag_fast <- function(rt_vector) {
  rt_vector <- threshold
}

flag_fast(experiment_data$rt) 

## Q5.2 Reveal the Bug----------
#rm(threshold)

## Q5.3 Debug and Fix It --------
flag_fast <- function(rt_vector) {
  rt_vector <- 500
}

```

#### Q6: Debugging Tools in Action -----------------------------
```{r}
## Q6.1 Reproduce the Issue --------
## NA messing things up - na.rm = TRUE

subject_means <- tapply(experiment_data$rt,
                        experiment_data$condition,
                        mean)
print(paste("Mean for control:", subject_means["control"]))
print(paste("Mean for incongruent:", subject_means["incongruent"]))

## Q6.2 Investigate Missingness --------------

# How many NAs overall?
sum(is.na(experiment_data$rt))

# How many NAs by condition?
tapply(is.na(experiment_data$rt), experiment_data$condition, sum)

## Q6.3 Fix the Calculation ----------
subject_means <- tapply(experiment_data$rt,
                        experiment_data$condition,
                        mean,
                        na.rm = TRUE)
print(paste("Mean for control:", subject_means["control"]))
print(paste("Mean for incongruent:", subject_means["incongruent"]))

```

#### Q7: Using AI for Debugging or Refactoring -----------------------
```{r}
## 7.1 Buggy Code --------
## redundant "ifelse"

# experiment_data$rt_category_vec <- ifelse(
#   is.na(experiment_data$rt), 
#    "Unknown", 
#   ifelse(classify_rt(experiment_data$rt_category_vec[i])
#    )
#  )

## 7.3 Working code -----------
experiment_data$rt_category_vec <- NULL

experiment_data$rt_category_vec <- ifelse(
  is.na(experiment_data$rt), 
  "Unknown", 
  sapply(experiment_data$rt, classify_rt)
)

```
#### Prompt---------

The error message is: Error in classify_rt(experiment_data$rt_category_vec[i]) : 
  Error: 'rt' must be numeric.
  
The problematic code is: 
experiment_data$rt_category_vec <- ifelse(
  is.na(experiment_data$rt), "Unknown", 
  ifelse(
  classify_rt(experiment_data$rt_category_vec[i])
   )
 )
 
 What I expected to happen: 
 I expected the code to fill rt_category_vec using using the classify_rt() function.

#### Evaluation: -----------

What did the AI do well?
ChatGPT gave me a fixed code that works, maintaining the vector ifelse() structure.  

What did you change or verify yourself?
This is a code that I was able to fix on my own earlier on in the problem set, and it was different than ChatGPT's revision. I realized that I did not need the second 'ifelse' because the ifelse function already has space to input 'if false'. 


How did you confirm the fix worked?
Initially, after I fixed this code in the earlier question of the pset, I ran the revised code again and saw that the rt_category_vec column was filled with "Slow", "Unknown", or "Fast". To check chatgpt's option, I deleted experiment_data$rt_category_vec, then ran ChatGPT's code. 

#### Q8: Saving and Reloading Objects -----------------------------
```{r}
## Q8.1 Cleaned Dataset ---------

##csv
write.csv(experiment_data, file = "../data/cleaned/experiment_data_revised.csv", row.names = FALSE)

##RDS
saveRDS(experiment_data, file = "../data/cleaned/experiment_data_revised.rds")

## Q8.2 Multiple Objects --------------
save(experiment_data, subject_means, file = "../data/cleaned/objects.RData")

##clearing environment...
rm(list = ls())

##...called object.RData back!
load("../data/cleaned/objects.RData")

```


